Universal Anonymous Signatures

### 2022-09-16 prism-backend/research/gsac/uas-paper.tex
In depth pass up to sec 3.1.

\usepackage[n,advantage,operators,sets,adversary,landau,probability,notions,
logic,ff,mm,primitives,events,complexity,asymptotics,keys]{cryptocode}
\usepackage{amssymb}
\usepackage{xspace}
\usepackage[normalem]{ulem}
\usepackage{hyperref}
\usepackage{mathtools}
\usepackage{multirow}
\usepackage{footnote}
\makesavenoteenv{tabular}
\makesavenoteenv{table}

%% Set/unset to activate/deactivate author comments
\def\authnotes{1}

@@

\begin{document}
{\def\addcontentsline#1#2#3{}\maketitle}%\maketitle

\begin{abstract}
  \todo{XXX}
\end{abstract}

>>>>

\usepackage[n,advantage,operators,sets,adversary,landau,probability,notions,
logic,ff,mm,primitives,events,complexity,asymptotics,keys]{cryptocode}
\usepackage{amssymb}
\usepackage{xspace}
\usepackage[normalem]{ulem}
\usepackage{hyperref}
%\usepackage{mathusertools}
\usepackage{multirow}
\usepackage{dashbox}

% Box types
\newcommand\dboxed[1]{\dbox{\ensuremath{#1}}}
\makeatletter
\newcommand{\dotboxed}[1]{%
\tikz[baseline={([yshift=-1ex]current bounding box.center)}] \node [rectangle, minimum width=1ex,dotted,draw,line width=0.6pt] {\normalcolor\m@th$\displaystyle#1$};}
\makeatother
\usepackage{footnote}
\usepackage{framed}
\usetikzlibrary{decorations.pathreplacing,calligraphy}
\makesavenoteenv{tabular}
\makesavenoteenv{table}

%% Set/unset to activate/deactivate author comments
\def\authnotes{0}

@@

\begin{document}
{\def\addcontentsline#1#2#3{}\maketitle}%\maketitle
\ifnum\authnotes=1
Version of \today
\fi

\begin{abstract}
  For decades, anonymous credentials (AC), group signatures (GS), and
  related schemes in the field of privacy-preserving authentication, have
  relied on common cryptographic tools. Yet, each has its own
  approach modelling-wise. Even within systems of the same type, multiple
  ``sub-models'' coexist, catering for slightly different needs.
  %
  Works like Camenisch et al (SAC'15) or Nguyen et al (CRYPTO'22)
  generalise some aspects, but still within their own domain -- AC and GS,
  respectively.

  In this work, we make a further effort in order to come up with a flexible
  game-based model that generalises and unifies GS and AC schemes. The key to
  this flexibility lies in functional placeholders
  that, with careful constraints, still allow to capture generalised notions of
  the usual anonymity, unforgeability and non-frameability properties. We refer
  to this unified model as \emph{Universal Anonymous Signatures} (\UAS).

  To showcase the generality of \UAS, we give a construction following our
  model and prove that, from it, we can easily build multiple
  variants of group signatures, anonymous credentials, and ring signatures, just
  by giving concrete definitions of the mentioned functional placeholders.

  Our main theoretical contribution is unifying previously separate (albeit
  close) systems under the same generalised model. Such unified model also
  allows to, very easily, build ``hybrid'' systems combining features
  of previously separately modelled constructions: e.g., anonymous credentials
  with conditional deanonymization based on their attributes.

  In practice, this means that cryptographic engineers and system designers
  can reach the desired utility-vs-privacy tradeoff that best suits their needs,
  just by defining a few functions -- but without needing to prove security from
  scratch or implement a whole system.
\end{abstract}
